An Embedding Framework for Consistent Polyhedral Surrogates

### 2022-05-11 poly-embed-journal/tikz/lovasz-links.tex
Cleaning up figures in section 5 and a pass on section 7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^*
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (1,1){\textbullet} (1,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,1)$};
\node at (1,0){\textbullet} (1,0)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1,0)$};
\node at (0,1){\textbullet} (-0.03,1)node[anchor= south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0,1)$};

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south west, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.3]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[thick,->, opacity=1] (-1.4,0) -- (1.4,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[thick,->, opacity=1] (0,-1.4) -- (0,1.4)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=south, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=south west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^*
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed, opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor= west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.1,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

@@

\node at (-1,-1){\textbullet} (-1,-1)node[anchor=north, minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,-1)$};
\node at (-1,0){\textbullet} (-1,0)node[anchor= south, minimum height = 0.7cm, scale = 0.4]{\tiny $(-1,0)$};
\node at (-1,1){\textbullet} (-1,1)node[anchor=south,  minimum height = 0.75cm, scale = 0.4]{\tiny $(-1,1)$};

\node at (0,-1){\textbullet} (-0.025,-1)node[anchor=north west,  minimum height = 0.75cm, scale = 0.4]{\tiny $(0, -1)$};
\node at (1,-1){\textbullet} (1,-1)node[anchor=north,  minimum height = 0.75cm, scale = 0.4]{\tiny $(1, -1)$};

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% \hat \Psi
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \psi^$\diamond$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tikzpicture}
\draw[dashed,opacity=0.2] (-1.2,0) -- (1.2,0) node[anchor=west, opacity=1]{\scriptsize $u_1$};
\draw[dashed, opacity=0.2] (0,-1.2) -- (0,1.2)node[anchor=south, opacity=1]{\scriptsize $u_2$};

%\draw[thick](.75,.75) -- (.75,.-.75) -- (-.75,-.75) -- (-.75,.75) -- cycle;
%% around 0,0
\draw[fill=limegreen, fill opacity = 0.8](.-0.25,.-0.25) -- (-.25,.25) -- (.25,.25) -- (.25,-.25) -- cycle;

%% around -1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,0.25) -- (-.75,-.25) -- (-1.2,-.25) -- (-1.2,.25) -- cycle;
\draw (-1.2,-.25) -- (-0.75,-0.25) -- (-.75,.25) -- (-1.2,.25);

%%around 1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,0.25) -- (.75,-.25) -- (1.2,-.25) -- (1.2,.25) -- cycle;
\draw (1.2,-.25) -- (0.75,-0.25) -- (.75,.25) -- (1.2,.25);

%% around 0,-1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.25,-0.75) -- (-0.25,-.75) -- (-.25,-1.2) -- (.25, -1.2) -- cycle;
\draw (-.25,-1.2) -- (-.25,-0.75) -- (.25,-.75) -- (.25,-1.2);

%%around 0,1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.25,0.75) -- (-.25,.75) -- (-0.25,1.2) -- (0.25,1.2) -- cycle;
\draw (-0.25,1.2) -- (-0.25,0.75) -- (0.25,.75) -- (.25,1.2);

%%around 1,1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,1.2) -- (.75,0.75) -- (1.2,0.75) -- (1.2,1.2) -- cycle;
\draw (1.2,0.75) -- (0.75,0.75) -- (.75,1.2);

%%around -1,1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,1.2) -- (-.75,0.75) -- (-1.2,0.75) -- (-1.2,1.2) -- cycle;
\draw (-1.2,0.75) -- (-0.75,0.75) -- (-.75,1.2);

%%around 1,-1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](0.75,-1.2) -- (.75,-0.75) -- (1.2,-0.75) -- (1.2,-1.2) -- cycle;
\draw (1.2,-0.75) -- (0.75,-0.75) -- (.75,-1.2);

%%around -1,-1
\draw[draw=none, fill=limegreen, fill opacity = 0.8](-0.75,-1.2) -- (-.75,-0.75) -- (-1.2,-0.75) -- (-1.2,-1.2) -- cycle;
\draw (-1.2,-0.75) -- (-0.75,-0.75) -- (-.75,-1.2);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% INDIFFERENT BETWEEN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% between 0,0 and -1,0
\draw[fill=limegreen, fill opacity = 0.2](-0.25,-0.25) -- (-.75,-.25) -- (-.75,.25) -- (-.25,.25) -- cycle;

%%between 0,0 and 1,0
\draw[fill=limegreen, fill opacity = 0.2](0.25,-0.25) -- (.75,-.25) -- (.75,.25) -- (.25,.25) -- cycle;

%% between 0,0 and 0,-1
\draw[fill=limegreen, fill opacity = 0.2](-0.25,-0.25) -- (-.25,-.75) -- (.25,-.75) -- (.25,-.25) -- cycle;

%%between 0,0 and 0,1
\draw[fill=limegreen, fill opacity = 0.2](-0.25,0.25) -- (-.25,.75) -- (.25,.75) -- (.25,.25) -- cycle;

%%between 1,1 and 0,1
\draw[draw=none, fill=limegreen, fill opacity = 0.2](0.75, 1.2) -- (.75, 0.75) -- (.25,.75) -- (.25,1.2) -- cycle;
\draw (0.25, 1.2) -- (0.25, 0.75) -- (.75,0.75) -- (0.75, 1.2);

%%between -1,1 and 0,1
\draw[draw=none, fill=limegreen, fill opacity = 0.2](-0.75, 1.2) -- (-.75, 0.75) -- (-.25,.75) -- (-.25,1.2) -- cycle;
\draw (-0.25, 1.2) -- (-0.25, 0.75) -- (-.75,0.75) -- (-0.75, 1.2);

%%between 1,-1 and 0,-1
\draw[draw=none, fill=limegreen, fill opacity = 0.2](0.75, -1.2) -- (.75, -0.75) -- (.25,-.75) -- (.25,-1.2) -- cycle;
\draw (0.25, -1.2) -- (0.25, -0.75) -- (.75,-0.75) -- (0.75, -1.2);

%%between -1,-1 and 0,-1
\draw[draw=none, fill=limegreen, fill opacity = 0.2](-0.75, -1.2) -- (-.75, -0.75) -- (-.25,-.75) -- (-.25,-1.2) -- cycle;
\draw (-0.25, -1.2) -- (-0.25, -0.75) -- (-.75,-0.75) -- (-0.75, -1.2);

%%between 1,1 and 1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.2](1.2, 0.75) -- (.75, 0.75) -- (.75,.25) -- (1.2,.25) -- cycle;
\draw (1.2,.25) -- (0.75, 0.25) -- (.75,0.75) -- (1.2, 0.75);

%%between -1,1 and -1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.2](-1.2, 0.75) -- (-.75, 0.75) -- (-.75,.25) -- (-1.2,.25) -- cycle;
\draw (-1.2,.25) -- (-0.75, 0.25) -- (-.75,0.75) -- (-1.2, 0.75);

%%between 1,-1 and 1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.2](1.2, -0.75) -- (.75, -0.75) -- (.75,-.25) -- (1.2,-.25) -- cycle;
\draw (1.2,-.25) -- (0.75, -0.25) -- (.75,-0.75) -- (1.2, -0.75);

%%between -1,-1 and -1,0
\draw[draw=none, fill=limegreen, fill opacity = 0.2](-1.2, -0.75) -- (-.75, -0.75) -- (-.75,-.25) -- (-1.2,-.25) -- cycle;
\draw (-1.2,-.25) -- (-0.75, -0.25) -- (-.75,-0.75) -- (-1.2, -0.75);

%%between 0,0 and 1,1
\draw[fill=limegreen, fill opacity = 0.2](.25,.25) -- (.5, .25) -- (.75,.5) -- (.75,.75) -- (.5,.75)-- (.25, .5) -- cycle;

%%between 0,0 and 1,-1
\draw[fill=limegreen, fill opacity = 0.2](.25,-.25) -- (.5, -.25) -- (.75,-.5) -- (.75,-.75) -- (.5,-.75)-- (.25, -.5) -- cycle;

%%between 0,0 and -1,1
\draw[fill=limegreen, fill opacity = 0.2](-.25,.25) -- (-.5, .25) -- (-.75,.5) -- (-.75,.75) -- (-.5,.75)-- (-.25, .5) -- cycle;

%%between 0,0 and -1,-1
\draw[fill=limegreen, fill opacity = 0.2](-.25,-.25) -- (-.5, -.25) -- (-.75,-.5) -- (-.75,-.75) -- (-.5,-.75)-- (-.25, -.5) -- cycle;

%%%%%%%%%%%%%%%%%%%%%%%%%
%%INDIFFERENT BETWEEN 3
%%%%%%%%%%%%%%%%%%%%%%%%%
%%between 0,0 and 1,0 and 1,1
\draw[fill=softyellow, fill opacity = 0.2](.5,.25) -- (.75, .25) -- (.75,.5) -- cycle;

%%between 0,0 and 0,1 and 1,1
\draw[fill=softyellow, fill opacity = 0.2](.25,.5) -- (.25, .75) -- (.5,.75) -- cycle;

%%between 0,0 and -1,0 and -1,1
\draw[fill=softyellow, fill opacity = 0.2](-.5,.25) -- (-.75, .25) -- (-.75,.5) -- cycle;

%%between 0,0 and 0,1 and -1,1
\draw[fill=softyellow, fill opacity = 0.2](-.25,.5) -- (-.25, .75) -- (-.5,.75) -- cycle;

%%between 0,0 and 1,0 and 1,-1
\draw[fill=softyellow, fill opacity = 0.2](.5,-.25) -- (.75, -.25) -- (.75,-.5) -- cycle;

%%between 0,0 and 0,-1 and 1,-1
\draw[fill=softyellow, fill opacity = 0.2](.25,-.5) -- (.25, -.75) -- (.5,-.75) -- cycle;

%%between 0,0 and -1,0 and -1,-1
\draw[fill=softyellow, fill opacity = 0.2](-.5,-.25) -- (-.75, -.25) -- (-.75,-.5) -- cycle;

%%between 0,0 and 0,-1 and -1,-1
\draw[fill=softyellow, fill opacity = 0.2](-.25,-.5) -- (-.25, -.75) -- (-.5,-.75) -- cycle;

%% embedding points
\node at (1,1){\textbullet};
\node at (1,0){\textbullet};
\node at (0,1){\textbullet};
\node at (-1,-1){\textbullet};
\node at (-1,0){\textbullet};
\node at (-1,1){\textbullet};
\node at (0,-1){\textbullet};
\node at (1,-1){\textbullet};
\node at (0,0){\textbullet};

%% envelope labels
%\node[scale=0.2] at (0.,0.13){(abs,abs)};
%\node[scale=0.2, text width=0.7cm] at (0.5,0.05){(abs,abs) OR (yes,abs)};
%\node[scale=0.2, text width=0.7cm] at (-0.53,-0.5){(abs,abs) OR (no,no)};
%\node[scale=0.2, text width=0.7cm] at (-1,0.5){(no,abs) OR (no,yes)};
\node[scale=0.2] at (0.,0.13){(0,0)};
\node[scale=0.2, text width=0.9cm] at (0.5,0.05){(0,0) OR (1,0)};
\node[scale=0.2, text width=1.05cm] at (-0.5,-0.5){(0,0) OR (-1,-1)};
\node[scale=0.2, text width=0.9cm] at (-1,0.5){(-1,0) OR (-1,1)};

%\node[scale=0.2] (3label) at (0.7, 1.25) {(abs,abs) OR (abs,yes) OR (yes,yes)};
\node[scale=0.2] (3label) at (0.7, 1.25) {(0,0) OR (0,1) OR (1,1)};
\node (3center) at (.325, 0.65) {};
\draw[->, blue] (3label) -- (3center.center);
